\subsection{Reflections}

Over the last couple of months I made a lot of mistakes whilst working with the project.
Was just not focusing enough or spending enough time to do the necessary research needed
to comprehend the topic. Moreover, I spent time focusing on the wrong aspects of my assignment.
An example of that is referred to the sections were we showed variants of our pure circuit
that have a combinatorial interpretation. Another core issue I faced was the lack
of experience when dealing with more theoretical based project. This led me to
trying to tackle the problem head on without exploring alternative avenues. For example 
we can observe that our main reduction from the \textit{EndOfLine} came
when using topological problems instead. 

\subsection{Lessons Learned}

Up to the current phase of our project, we were able to gather several important takeaways.
Exploring the literature and trying to work the problem under different perspectives
may lead to potential breakthroughs. The main catalyst to our core finding, came
when looking into problems such as \textsc{EOPL} or more specifically
the \textsc{OPDC} problem, described by Fernley et al. \cite{fearnley_unique_2020}.
\textsc{OPDC} can be described as a simpler version of the traditonal n-dimensional Brouwer problem
where instead, we have a unqiue fixed point and our function will point towards the unique solution.
Moreover, deeper look into Kleene-logic or more specifically \textit{Hazard-free} circuits allowed
us to exploit the $\bot$ value to compute multiple input simultaneously \cite{ikenmeyer_complexity_2019}.
Using the two aforementioned observations as well as looking at the original reduction again allowed us to achieve
the desired breakthrough.

In order to accomplish the above research, we have also learned how to research more effectively.
Exploitation of LLMs such as \texttt{ChatGPT}, \texttt{Perplexity} and more, we are able to
approach the problem from multiple perspectives. Moreover, thought organisation and cataloguing with
\texttt{Obsidian}
also came crucial when handling a large volume of ideas and information over a long period of time,
as explained in the previous sections. Last but not least, utilisation of books,
related research and textbooks also came important when it came to theory crafting and idea extraction.

Last but not least, the general approach to the project changed over the course of time.
Understanding that the journey of discovery as important as the discovery itself,
made the project more enjoyable. Having the freedom to explore areas and expand
the horizons of what we know, is what keeps this project exhilarating.
Ultimately, this mindset helped the project stay engaging and allowed for continuous learning throughout.




