Combinatronics has been a field of study in mathematics that primarily focuses on
the notion of counting objects with certain properties. Over time, this notion
has shifted, especially in the subfield of algebraic combinatorics, where
there is no clear notion of the object that we are counting,
and the numbers express something more abstract \cite{pak_WhatCombinatorialInterpretation_2022}.
In recent years, there has been a revolutionary
initiative in the field of combinatronics to assign combinatorial interpretations to such numbers.
Being able to find such definitions or interpretations is very important
as it allows us to utilise tools from combinatorics to understand
and reveal hidden structures and properties \cite{pak_WhatCombinatorialInterpretation_2022}. 
Moreover, there are several problems or numbers such as \textit{Kronecker coefficients} \cite{makar_AnalysisKroneckerProduct_1949},
whose combinatorial interpretation, would lead to groundbreaking breakthroughs such as a step closer to the resolution of the $\textit{P} \neq \textit{NP}$
conjecture \cite{ikenmeyer_WhatWhatNot_2022, ikenmeyer_VanishingKroneckerCoefficients_2017}.


% To formalise that idea, Pak et al. has argued that if a function $f$
% belongs to $\textit{\#P}$, it implies that $f$ has a combinatorial interpretation
% \cite{pak_WhatCombinatorialInterpretation_2022, ikenmeyer_WhatWhatNot_2022}. We invest
In our current work, we focus on extending the work done by
Ikenmeyer et al. \cite{ikenmeyer_WhatWhatNot_2022}, where they focused on the creation of frameworks
that determines whether $f \in^? \textsc{\#P}$, by looking
at the subclasses of $\textsc{\#TFNP - 1}$ problems.
In our work we focus specifically on the complexity class of $\textsc{PPAD}$, under the lens of $\text{PureCircuit}$,
due to circuit-based nature.
We hope to uncover many insights of the $\textsc{\#PureCircuit} -1$ problem 
as well as explore the boundaries of $\textsc{\#PPAD} -1$.

% In their paper, they were able to show that for a subclass of
% problems, also known as $\textit{PPAD} \subseteq \textit{TFNP}$,
% different $\textit{PPAD-complete}$ problems, may or may not have a combinatorial
% interpretation.

\subsection{Research Question}

Our objectives revolve around the conjecture in \ref{conj:ppad-1-hardness}, where
we investigate the boundaries of $\scn{\#PPAD}-1$ with the help of the \textsc{PureCircuit} problem.
\begin{conjecturebox}{$\scn{\#PPAD}-1$ hardness}{ppad-1-hardness}
    Every language in \scn{PPAD} can be parsimoniously reduced up to some polynomial factor, to the
    \textsc{PureCircuit} problem, or more formally:
    $$
    \forall L \in \scn{PPAD}, \exists f \in n^{O(1)}: 
    \scn{\#L} \subseteq^f \scn{\#PureCircuit}
    $$
\end{conjecturebox}




\subsection{Project objectives}

To tackle our research question, we propose the following list of objectives. 
These objectives outline a series of reductions between problems that were identified as necessary,
as explained in paragraph \ref{par:count-ppad}.
We hope that by completing these milestones, we will be able to answer our research question.

\begin{enumerate}[label*=R.\arabic*)]
    \item Find a parsimonious reduction from the $\textsc{EndOfLine}$ to $\textsc{PureCircuit}$.
    \item Demonstrate that $\textsc{\#PureCircuit}- 1 \not\subseteq \textsc{\#P}$ either by:
        \begin{enumerate}
            \item Showing that $\textsc{\#SourceOrExcess(k,1)} \subseteq \textsc{\#PureCircuit}$ for some $k \in \mathbb{N}_{\geq 2}$
            \item Showing that $\textsc{\#SourceOrExcess(k,1)} \subseteq \textsc{\#nD-StrongSperner}$ for some $k,n \in \mathbb{N}_{\geq 2}$ 
        \end{enumerate}
    \item Prove or disprove the following:
\[
\forall n \in \mathbb{N}_{\geq 2}, \exists c \in \mathbb{N}:  \scn{\#SourceOrExcess}(n, 1) \subseteq^c \scn{\#PureCircuit}
\]

\end{enumerate}

In addition to expanding the theory of $\textsc{\#PPAD} -1$, we aim to build
a visualisation tool for $\textsc{PureCircuit}$ instances. This tool
will allow us to visualise circuits as well as investigate the behaviour
of $\textsc{PureCircuit}$ for controlled cases. More formally,
we have the following milestones:

\begin{enumerate}[label=S.\arabic*)]
    \item Visualise and verify a \textsc{PureCircuit} instance.
    \item Generate a solution for given a \textsc{PureCircuit} instance.
    \item Count the number of solutions of a \textsc{PureCircuit} instance.
\end{enumerate}

We will compile the rest of the report, based on our current findings, how we altered our previous objectives 
and general reflections. Moreover we will give a brief summary as to the subsequent steps
and how plan to achieve the remaining milestones.


%
% Below we will present our main list of findings up to this point:
%
% \begin{theorem}[ND-Brouwer to PureCircuit]
%     Given $f(x) \triangleq 20$
%     $$
%     \scn{\#Brouwer}^{f_3} \subset^f \scn{\#PureCircuit}
%     $$
% \end{theorem}
%
% \begin{corollary}
%     For any $d \in \mathbb{N}_{\geq 2}$, we can define $f(\cdot) = \sum_{i = 1}^{d -1}  \binom{d}{i} 2^i$
%     such that:
%     $$
%     \scn{\#Brouwer}^{d} \subset^f \scn{\#PureCircuit}
%     $$ 
% \end{corollary}
%
%
%
% \begin{theorem}
%     For any $d \in \mathbb{N}_{\geq 2}$, we can define $f(\cdot) = 5$
%     such that:
%     $$
%     \scn{\#Brouwer}^d \subseteq^f \scn{\#PureCircuit}
%     $$ 
% \end{theorem}
%
%
% Throughout our search, we stumbled upon
% various variants of the problem as well as reductions and claims from other
% subclasses of PPAD or Hazard-Free logic
%
% \begin{proposition}
%     Weaker variants of PureCircuit can result to parsimonious reductions to the EndOfLine problem
%     as such:
%     \begin{gather*}
%         \scn{\#AcyclicBPureCircuit} \subseteq \scn{\#EndOfLine} \\
%         \scn{\#PermutationFreeBPureCircuit} \subseteq \scn{\#EndOfLine}
%     \end{gather*}
% \end{proposition}
%
%
% In addition, we were able to show that for different promise problems,
% we can find reductions to the PureCircuit problem
% %
% \begin{proposition}
%     $$
%         \scn{\#PUnsatHazard} \subseteq  \scn{\#PureCircuit}
%     $$
% \end{proposition}
%
% Lastly we introduce the following proposition
% \begin{proposition}
%     Given function $F: \mathbb{T}^n \to \mathbb{T}^n$
%     where $\mathbb{T} \triangleq \{0, 1, \bot\}$ and $F$ is a \textbf{natural}
%     function:
% $$
% \exists x^\star \in \mathbb{T}^n: F(x^\star) = x^\star
% $$
% \end{proposition}
% %
%
% The idea above is based on the Tarski Fixed point theorem.
% Using fixed points with the Kleene logic set, has been used in the past
% by Kozer as seen in his book \cite{kozen2006theory}, but we
% are extending such ideas to any possible functions or gates
% that use monotone gates. Doing that allows us to make the following observation.
%
% \begin{proposition}
%     $$
%     \scn{\#HazardTarski} \subseteq \scn{\#PureCircuit}
%     $$
% \end{proposition}
%
